Reproducible Research Project 1
========================================================

Loading and preprocessing the data.

```{r}
#setwd("./Reproducible Research")
data <- read.csv("activity.csv")
```

Mean total number of steps taken per day.

```{r}
library(plyr)
library(lattice)
data2 <- ddply(data, .(date), summarise, total_steps = sum(steps,na.rm = T))
histogram(data2$total_steps, main = "Histogram of the total number of steps taken each day", xlab = "Total steps")
mean <- mean(data2$total_steps)
median <- median(data2$total_steps)
```

Show the mean and median of steps taken per day.

```{r}
mean
median
```

Calculating and plotting average number of steps taken averaged across all days.

```{r}
meancross <- ddply(data, .(interval), summarise, average_steps = mean(steps,na.rm = T))
xyplot(meancross$average_steps~meancross$interval, type = "l", xlab = "5-minute interval", ylab = "Average number of steps taken")
# The interval contains the maximum number of steps is:
meancross$interval[which(meancross$average_steps == max(meancross$average_steps))]
```

Calculate and report the total number of missing values in the dataset.

```{r}
logical <- is.na(data)
result <- rep(0,length(logical[,1]))
for(i in 1:length(result))
        if(logical[i,1] == TRUE)
                result[i] = 1
sum(result)
```

Filling missing values using mean for that 5-minute interval.

```{r}
for(i in 1:length(result))
        if(is.na(data[i,1]))
                data[i,1] = meancross[which(data[i,3] == meancross$interval), 2]
        
```

Histogram of the total number of steps taken each day based on new dataset.

```{r}
data3 <- ddply(data, .(date), summarise, total_steps = sum(steps))
histogram(data2$total_steps, main = "Histogram of the total number of steps taken each day", xlab = "Total steps")
mean2 <- mean(data3$total_steps)
median2 <- median(data3$total_steps)
```

Show the mean and median of steps taken per day.

```{r}
mean2
median2
```

Creat factor variable indicating whether a given date is a weekday or weekend.

```{r}
weekday <- rep("",length(result))
for(i in 1:length(weekday))
        if(weekdays(as.Date(data[i,2])) == "ÐÇÆÚÁù" | weekdays(as.Date(data[i,2])) == "ÐÇÆÚÈÕ"){
                weekday[i] <- "weekend"}else{
                weekday[i] <- "weekday"}
data4 <- cbind(data, weekday)
data5 <- ddply(data4, .(interval, weekday), summarise, average_steps = mean(steps))
```

Make a panel plot.

```{r}
xyplot(average_steps~interval|weekday, data = data5, layout = c(1,2), ylab = "Number of steps", type = "l")
```
